Hemodynamic responses of the anterior "parahippocampal place area" (PPA) to a Hollywood movie's audio-description

### 2020-12-07 paper/main.tex
revise descriptions of contrasts v2

\todo[inline]{SE: habe mich mit 2.8 extrem schwer getan: Länge des Abschnitts,
oft komplizierten Beschreibungen}

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator. These categories served as a basis to
        build the regressors of the GLM (cf. Table \ref{tab:ao-events}).
        Examples are given in English.
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms (insides) or  locales (outsides) & living room; wall, door,
window, floor, turf
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\todo[inline]{SE: Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
    COH: I dropped the table of counts per segment.  The information is
    redundant since the counts are not the count of events of the actual
regressors (cf. Table \ref{tab:av-events})}

@@

groom & elements defining geometry of room & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII

@@

\todo[inline]{SE: das mit den "five additional categories" habe ich nicht
verstanden. Überhaupt finde ich die ganze Beschreibung relativ schwer zu
durchdrungen, und ich glaube damit werde ich nicht alleine sein. COH: }
% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

vno\_cut & a continuous frame from the same camera position & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII

@@

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AO stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition and to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter}

\todo[inline]{Habe jetzt lange darüber gebrütet: Es gibt also kaum eine
Korrelation zwischen AO und AV?; Also, außer bei fg\_av\_ger\_lr\_diff (wobei da
keiner weiss, was das bedeutet)}

@@

% why several contrasts
To test the robustness of our approach,  we created several contrasts for every
stimulus.
%
We operationalized the perception of spatial information compared to the
perception of ``non-spatial'' information differently in eight $t$-contrasts for
the AO stimulus (see Table \ref{tab:ao-contrasts}) and five $t$-contrasts for
the AV stimulus (see Table \ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in \todo{differ in what?
``localization performance'' isn't well phrased. How ``well'', ``nice'' the
results are?} since used event categories differed a) in how well the averaged
events reflected spatial information, and b) in event counts
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the primary contrast of the AO stimulus we contrasted \texttt{geo} and
\texttt{groom} with all non-geometry related categories
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
In the primary contrast of the AV stimulus we contrasted

% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

% for example, AO stimulus AO COPEs: intro
For example, the categories \texttt{se\_new} and \texttt{se\_old} of the AO
stimulus were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast.
%
In a serial stream of auditory information, these nouns could be perceived
differently by different subjects as either a geometry-defining scene elements
or as an isolated object.

% why not locale change

@@

% intro

% AO
Five $t$-contrasts (see Table \ref{tab:ao-contrasts}) we created as negative
controls to test if increased activation in the PPA was correlated with moments
of cuts and therefore possibly correlated with a accompanying change in the
soundscape.

% AV
% negative control
Five additional $t$-contrasts we created for negative control purposes (see
Table \ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AO).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old & non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie (AV).
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator cues the
    listener about a switch of settings, events that could be correlated with a
    switch of the soundscape.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for narrator \tabularnewline
\end{tabular}
\end{table*}

>>>>

@@

% table for descriptive nouns: categories, rules, examples counts
\begin{table*}[h!]
    \caption{Categories and rules to categorize the descriptive nouns spoken by
        the audio-description's narrator. These categories served as a basis to
        build the regressors of the GLM (cf. Table \ref{tab:ao-events}).
        Examples are given in English.
        % The category \texttt{++} also contains adverbial of time.
}
\label{tab:descr-nouns-rules}
\begin{tabular}{lll}
\toprule
\textbf{category} & \textbf{rule} & \textbf{examples} \\
\midrule
body & trunk of the body; overlaid clothes & back, hip, shoulder; jacket, dress, shirt
\tabularnewline
bodypart & limbs and trousers & arm, finger, leg, toe
\tabularnewline
face & face or parts of it & face, ear, nose, mouth
\tabularnewline
female & female person & nurse, mother, woman
\tabularnewline
females & female persons & women
\tabularnewline
fname & female name & Jenny
\tabularnewline
furniture & movable furniture insides \& outsides & bench, bed, table, chair
\tabularnewline
geo & immobile landmarks & building, tree, street, alley, meadow, cornfield \tabularnewline
geo-room & rooms \& locales or geometry-defining elements & living room; wall, door, window, floor
\tabularnewline
head & non-face parts of the head; worn headgear & head, hair, ear, neck,
helmet
\tabularnewline
male & male person & man, father, soldier
\tabularnewline
males & male persons & boys, opponents
\tabularnewline
mname & male name & Bubba, Kennedy
\tabularnewline
object & countable entity with firm boundaries & telephone, car
\tabularnewline
objects & countable entities & wheels, plants
\tabularnewline
persons & concrete persons of unknown sex & hippies, patients
\tabularnewline
setting\_new & a setting occurring for the first time & on a ``bridge'', on an ``alley'', on ``campus''
\tabularnewline
setting\_rec & a recurring setting & at the ``bus stop'' \tabularnewline
% ++ & cue regarding time & in the ``evening'', it's ``daytime'', ``later'' \tabularnewline
\bottomrule
\end{tabular}
\end{table*}

\todo[inline]{SE: Table 2 ist relativ kryptisch bzw für jemanden, der sich zum
    ersten Mal damit auseinander setzt kaum zu verstehen. Auch ist der Bezug zum
    GLM unklar, d.h., was davon wird verwendet und was verbirgt sich dahinter;
    COH: I dropped the table of counts per segment.  The information is
    redundant since the counts are not the counts of events of the actual
regressors (cf. Table \ref{tab:av-events})}

@@

groom & rooms \& locales or geometry-defining elements & \aoGroomAll & \aoGroomI & \aoGroomII & \aoGroomIII & \aoGroomIV & \aoGroomV & \aoGroomVI & \aoGroomVII & \aoGroomVIII

@@

% categories taken from movie cut annotation
To create contrasts of cross-modal negative control and to capture variance of a
possibly confounding change of the soundscape after a cut, we also implemented
the five movie cut-related regressors used in the GLM of the AV stimulus (see
details below) in the model of the AO stimulus.
% nuisance regressors
\todo[inline]{"Continuous bins lasting 40ms" ?!?; COH: goddamnit! I've rewritten
    this explanation a lot and finally stuck to the phrasing written in
    \citep{wilson2008beyond} who did the same; it is rephrased now though}
%
Lastly, we created two nuisance regressors based on left-right difference in
volume and root mean square energy averaged across the length of every movie
frame (\unit[40]{ms}) to capture variance correlating with low-level perceptual
processes.
% Reference to table
An overview and the respective counts of the eleven speech-related event
categories, the five movie cut-related categories, and the two low-level
confounds can be found in Table \ref{tab:ao-events}.
% convolving
Events for all regressors of the AV stimulus were convolved with a
double gamma hemodynamic response function (HRF).

@@

vno\_cut & frames within a continuous movie shot & \avVnocutAll & \avVnocutI & \avVnocutII & 0 & \avVnocutIII & \avVnocutIV & \avVnocutV & \avVnocutVI & \avVnocutVII

@@

% irrespectible of visual content
Notably, categorization was performed irrespectively of a movie frame's precise
content and thus without controlling confounding variables (e.g. presence of
faces).
% AV COPEs: intro
The rationale that this approach would still yield categories correlating with
increased hemodynamic activity in the PPA was twofold.
% cinematographic rationale cut to new scenes: establishing shots
The cinematographic rationale was that movies tend to establish the setting
(\texttt{vse\_new}) and the spatial relationships within a setting
(\texttt{vpe\_new}) at the beginning of a movie.
% cut to recurrent scene
Later in the movie, the field sizes of movie shots tend to decrease when
switching back to already established settings (\texttt{vse\_old}).
% similarly for shots within a scene
Moreover, shots within a recurring locale or setting tend to shift to depicting
persons and objects (\texttt{vpe\_old}) more relevant to the evolved plot
\citep{brown2012cinematography, mercado2011filmmakers}.
% neuroscientific rationale
The neuroscientific rationale was that activity in the PPA is greater when
participants view novel versus repeated scenes or view-points.
\citep{epstein1999parahippocampal, grill2006repetition}.
% null regressor
As for the regressors for AO stimulus, a null regressor was chosen for a
regressor in a segment if that segment did not contain an event of the
corresponding category.
% no cut condition: intro
A sixth regressors of pseudo-randomly chosen frames (\texttt{no\_cut}) was
created as a control condition to create negative control contrasts:
% procedure
Frames were drawn from movie shots lasting at least \unit[20]{s} and had to have
a minimum distance of \unit[10]{s} to a movie cut and to another
\texttt{no\_cut} event.

@@

\todo[inline]{Die Abkürzungen in Figure 1: Da steigt keiner hinter; habe jetzt
lange darüber gebrütet: Es gibt also kaum eine Korrelation zwischen AO und AV?;
Also, außer bei fg\_av\_ger\_lr\_diff (wobei da keiner weiss, was das bedeutet)}

@@

% intro
To test the robustness our approach, we operationalized the perception of
spatial information compared to the perception of ``non-spatial'' information
differently in eight $t$-contrasts for the AO stimulus (see Table
\ref{tab:ao-contrasts}) and five $t$-contrasts for the AV stimulus (see Table
\ref{tab:av-contrasts}).
% reason: robustness
We assumed all contrasts could in principle correlate with increased hemodynamic
activity in the PPA.
% but we expect differences because
Nevertheless, we also assumed contrasts would differ in [?] \todo{differ in
what?  ``localization performance'' isn't well phrased. How ``well'', ``nice''
the results are?} since the event categories differed a) in how well the
averaged events reflected spatial information, and b) in event counts.
% thus: primary contrasts
We chose one ``primary contrast'' for every stimulus before running the
analyses.
% selection criteria for primary contrast.
The selection criterion for the primary contrast of each stimulus was a
subjectively good balance between a) how well categories on average were assumed
to match the preferred stimulus type, and b) the amount of available data /
events.\todo{oh, lord!}

% AO: primary contrast
In the primary contrast of the AO stimulus, we contrasted landmarks
\texttt{geo}, and rooms and geometry-defining objects \texttt{geo-room} with all non-geometry related categories (\texttt{body},
\texttt{bodypart}, \texttt{fahead}, \texttt{object}, \texttt{sex\_f},
\texttt{sex\_m}) except \texttt{furniture}.

% why se_new & se_old were not used in the primary contrasts
The categories of nouns cueing a setting that occured for the first time
(\texttt{se\_new}) or a setting that recurred during the plot (\texttt{se\_old})
were not included in the primary contrast because
% heterogeneous category
a) categories comprise words that could count as a member of another category
(e.g. ``[a] physician''),
% richness of verbal description vs. picture
b) nouns only vaguely described a scene (e.g. ``[in] Greenbow'', ``[in a]
disco'', ''[black and white] film recordings'') [compared to whole, perceptually
richer pictures], and
% hierarchical categories
c) the narrator is often lacking behind a short dialogue or a change of the
soundscape that might already cued a change of settings.
% furniture
The category ``furniture'' (\texttt{furn}) was not used as a regressor of
interest in any contrast because these nouns could be perceived differently by
different subjects as either a geometry-defining scene element or as an isolated
object.

% AV primary contrast
In the primary contrast of the AV stimulus, we contrasted cuts to a setting that
was not depicted before (\texttt{vs\_new}) to cuts that we accompanied with a
change of the camera position within a setting that was already occurring
previously (\texttt{vpe\_old}).
% why
We assumed these categories on average best represent events that trigger
perception of space versus objects or faces.\todo{syntax?}

@@

% intro
Finally, we created several contrasts as negative control for both stimuli.
% AO stimulus
For the AO stimulus, we created five $t$-contrasts (see Table
\ref{tab:ao-contrasts}) to test if increased activation in the PPA was
correlated with moments of cuts possibly correlated with a accompanying change
in the soundscape.
% AV stimulus
For the AV stimulus, four $t$-contrasts were created contrasting the no-cut
condition (texttt{vno\_cut} for negative control purposes (see Table
\ref{tab:av-contrasts}) by using regressors based on regressors of the AO
stimulus. One contrast (\texttt{vs\_new} > \texttt{vpe\_old})  was created by
contrasting nouns spoken by the narrator.

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the audio-only
    stimulus (AO).
    Contrast 1-8 aim to isolate the PPA.
    \texttt{non-spatial categories} refers to the to the categories
    \texttt{body}, \texttt{bodypart}, \texttt{fahead},
    \texttt{object}, \texttt{sex\_f}, \texttt{sex\_m}.
    Contrasts 9-13 serve as negative control contrasts at the moments of movie
    cuts (see Table \ref{tab:av-contrasts}).}
\label{tab:ao-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & geo, groom > non-spatial categories & PPA \tabularnewline
2 & geo, groom, se\_new > non-spatial categories & PPA \tabularnewline
3 & groom, se\_new, se\_old > non-spatial  & PPA \tabularnewline
4 & geo > non-spatial categories & PPA \tabularnewline
5 & groom > non-spatial categories & PPA \tabularnewline
6 & se\_new > non-spatial categories & PPA \tabularnewline
7 & se\_new, se\_old > non-spatial categories & PPA \tabularnewline
8 & se\_new > se\_old > non-spatial categories & PPA \tabularnewline
9 & vse\_new > vpe\_old & control at moments of cuts \tabularnewline
10 & vse\_new, vpe\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
11 & vse\_new > vse\_old & control at moments of cuts \tabularnewline
12 & vse\_new > vse\_old, vpe\_old & control at moments of cuts \tabularnewline
13 & vse\_new, vpe\_new > vpe\_old & control at moments of cuts \tabularnewline
\end{tabular}
\end{table*}

\begin{table*}[h!]
\caption{Contrasts of parameter estimates for the analysis of the
    audio-visual movie (AV).
    Contrast 1-5 aim to isolate the PPA.
    Contrast 6-9 serve as negative control.
    Contrast 10 serves as control for moments when the narrator cues the
    listener about a switch of settings, events that could be correlated with a
    change of the soundscape.}
\label{tab:av-contrasts}
\footnotesize
\begin{tabular}{lll}
\toprule
\textbf{nr.} &  \textbf{contrast} & \textbf{purpose} \\
\midrule
1 & vse\_new > vpe\_old & PPA \tabularnewline
2 & vse\_new, vpe\_new > vse\_old, vpe\_old & PPA \tabularnewline
3 & vse\_new > vse\_old & PPA \tabularnewline
4 & vse\_new > vse\_old, vpe\_old & PPA \tabularnewline
5 & vse\_new, vpe\_new > vpe\_old & PPA \tabularnewline
6 & vno\_cut > vse\_new & negative control \tabularnewline
7 & vno\_cut > vse\_old & negative control \tabularnewline
8 & vno\_cut > vse\_new, vse\_old & negative control \tabularnewline
9 & vno\_cut > vpe\_new, vpe\_old & negative control \tabularnewline
10 & se\_new > se\_old & control for (missing) narrator \tabularnewline
\end{tabular}
\end{table*}
